{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} y_k\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.

@@

                \Vert \mathcal G_{1/L_k} y_k\Vert 

@@

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

            f(x_m) - f(x_k) \le \exp(-1)(f(x_0) - f(x_m)). 

@@

@@

        $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop and, it has $p_j \ge n_{j}$. 

@@

        Consequently, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j$ or $p_{j + 1} \ge n_{j + 1} = p_j$. 

@@

        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $z_{j, k}$ for the iterates $x_k$ in the inner loop and $z_j$ in the outer loop together. 
        We make the choice to have $z_{j + 1, -1} = z_{j, p_j} = z_{j + 1}$ for consistencies across theorems from previous sections. 
        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. Denote $x_{p_j}$ as $z_{j, p_j}$ and, it's assigned to $z_{j + 1}$ by the outer loop so $x_{p_j} = z_{j, p_j} = z_{j + 1}$. 
        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =z_{j + 1, -1}$. 

@@

            We make the following assumption first and it will be proved later:

@@

        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a for $p_j$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates. 

@@

@@

            Let $(z_{j,k})_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p$. 

@@

            We now have the base case: $p_0 \le p_1 \le \bar p$. 

@@

            Therefore, for all $j \ge 0$, $p_j \le \bar p$. 

@@

            Starting with the statement hypothesis it has $k \ge \ bar p$ therefore: 

@@

                \right\rfloor

@@

                e^{-1} \ge \frac{F(z_{j, m}) - F^+}{F(z_{j, -1}) - F(z_{j, m})} \ge \frac{F(z_{j, m}) - F(z_{j, k})}{F(z_{j, -1}) - F(z_{j, m})} \implies \mathbf E_{\chi}^a. 
            Observe that line 11 of Algorithm \ref{alg:gmapg} exits as soon as possible if $E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore $p_j \le \max(\bar p, n_j)$. 

@@

            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 

@@

                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} \ge \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 

@@

                e^{-1} \ge \frac{F(z_{j - 1, p_{j - 1}}) - F^+}
                {F(z_{j - 1, -1}) - F(z_{j - 1, p_{j - 1}})}

@@

        \begin{theorem}[bounds on the total iterations]
            ...
        \end{theorem}

>>>>

                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} (y_k)\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.

@@

                \Vert \mathcal G_{1/L_k} (y_k)\Vert 

@@

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                    \STATE{\noindent
                        \textbf{Function GMAPG Inputs: }
                        \begin{tabular}{|ll}
                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\
                            $g: \RR^n \rightarrow \overline\RR$ & Weakly Convex \\ 
                            $x_{-1}$ & Vector\\
                            $L\in \RR$ & $L > 0$\\ 
                            $r $ & $r \in (0, 1)$ \\ 
                            $\rho \in \RR$ & $\rho \in (0, 1)$ \\
                            $N_{\min}\in \N$ & $N \ge 1$ \\
                            $N \in \N$ & $N \ge N_{\min}$ \\
                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 
                        \end{tabular}
                    }
                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = \Vert \sqrt{L_0}(x_0 - y_0)\Vert.$}
                    \IF{$G_0 \le \epsilon$}
                        \STATE{\textbf{Return: }$x_k, 0, L_0, G_0$}
                    \ENDIF
                    \FOR{$k := 1, 2,\ldots, N$}
                        \STATE{\noindent
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                        }
                        \STATE{$\overline L := \max(L_k, L_{k - 1})$. }
                        \STATE{\noindent
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        }
                        \STATE{$G_k:= \Vert \sqrt L_k(\tilde x_k - y_k)\Vert $}
                        \STATE{\noindent
                            $x_k, \eta_{k + 1}, G_k^+ := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        }
                        \IF{$G_k^+ < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                            \STATE{\textbf{break}}
                        \ENDIF
                    \ENDFOR
                    \STATE{\textbf{Return: }$x_k, k, \overline L, G_k^+ $}
                \caption{GMAPG with Chambolle's backtracking}\label{alg:gmapg}
                \end{algorithmic}
            \end{algorithm}
            The above Algorithm \ref{alg:gmapg} is an implementation of GMAPG in Definition \ref{alg:gmapg}. 
            Parameters $r, \rho$ are chosen in the discretion of the practitioners. 
            For example, we chose $r= 0.4, \rho = 2^{1/1024}$.

@@

            f(x_m) - f(x_k) \le \exp(-1)(f(x_{-1}) - f(x_m)). 

@@

        \begin{observation}
            If the outer loop runs for $j = 1, 2, \ldots, J$ iterations with $M \ge J$ so the algorithm terminated due $G_k^+ \le \epsilon$. 
            Then for all $J\ge j\ge 1$ it has $n_{j}\le n_{j + 1}$ hence $(n_j)_{j \ge 0}^J$ is monotone increasing
            For all $J -1 \ge j \ge 1 $ it has $p_{j-1}\le p_{j}$ so $(p_j)_{j \ge 1}^{J}$ is monotone exluding the last iterates $p_J$. 
        \end{observation}

@@

        For all $1 \le j \le J$, $n_j$ is used as the lower bound $N_{\min}$ for the GMAPG inner loop described in Algorithm \ref{alg:gmapg} at iteration $j$ and, $p_j$ is the actual iteration underwent by the inner loop therefore it has $p_j \ge n_{j}$. 

@@

        For $j < J$ so it excludes the last iteration, it has either $p_{j + 1} \ge n_{j + 1} = 2p_j \ge 2n_{j} \ge n_j$ or $p_{j + 1} \ge n_{j + 1} = p_j \ge n_j$. 
        When $j = J$ it's not necessarily true that $p_J \ge n_J$ because on the last iteration, it can exit the forloop through conditions $G_k^+ \le \epsilon$ in line 14 of Algorithm \ref{alg:gmapg}, but $n_J \ge p_{J - 1} \ge n_{J - 1}$ still. 

@@

        Since the restarted GMAPG consist of executions of an outer loop in Algorithm \ref{alg:linear-rgmapg} in variable $j$ and, an inner loop in Algorithm \ref{alg:gmapg} in variable $k$, we denote $x_{k}^{(j)}$ for the iterates $x_k$ in the inner loop during the $j$ iteration of the outer loop together. 
        We make the choice to have $x_{-1}^{(j + 1)} = z_{j + 1} = x_{p_j}^{(j)}$ for consistencies across theorems from previous sections. 
        For example in line 7 of Algorithm \ref{alg:linear-rgmapg} at the $j$ iteration, the inner loop returns $x_{p_j}$ as the last iterate. 
        So $x_{p_j}$ is assigned to assigned to $z_{j + 1}$ by the outer loop and it has $x_{p_j} = x_{p_j}^{(j)} = z_{j + 1}$. 
        It continues and $z_{j + 1}$ will be the initial iterate pass into the inner loop for the $j + 1$ iteration, and hence $z_{j + 1} =x_{-1}^{(j + 1)}$. 

@@

            We make the following assumption first, and it will be proved later:

@@

        Continuing with the quadratic growth assumption, the following lemma states the fact that $p_j$ in Algorithm \ref{alg:linear-rgmapg} is bounded above and there exists a $j \ge 1$ such that $n_{j + 1 + k} = p_{j + k}$ for all $k \ge 0$ until it terminates. 

@@

            Suppose that $F = f + g$ satisfies Assumption \ref{ass:standard-fista} and Assumption \ref{ass:q-growth-ch2}, denote $F^+ := \inf_xF(x)$ and, $X^+$ as the set of minimizers. 

@@

            Let $\left(x_{k}^{(j)}\right)_{k\ge 0}^{p_{j}}$ be the sequence generated by Algorithm \ref{alg:linear-rgmapg} in the $j$ th iteration of outer loop. 
            Define $\bar p := \frac{4\sqrt{2L(1 + e)}}{\sqrt{\mu}}$, then $p_{j} \le \bar p, n_j \le \bar p$. 

@@

            We now have the base case: $p_0 \le p_1 = n_0 \le \bar p$. 

@@

            Therefore, for all $j \ge 0$, $p_j \le \bar p$, and $n_{j + 1} \le \bar p$. 

@@

            Starting with the statement hypothesis it has $k \ge \bar p$ therefore: 

@@

                \right\rfloor. 

@@

                e^{-1} \ge 
                \frac{
                    F\left(x_{m}^{(j)}\right) - F^+
                }{
                    F\left(x_{-1}^{(j)}\right) 
                    - F\left(x_{m}^{(j)}\right)
                \frac{
                    F\left(x_{m}^{(j)}\right)
                    - F\left(x_k^{(j)}\right)
                }{
                    F\left(x_{-1}^{(j)}\right) 
                    - F\left(x_{m}^{(j)}\right)
                \implies \mathbf E_{\chi}^a. 
            Observe that line 14 of Algorithm \ref{alg:gmapg} exits as soon as possible if $\mathbf E_\chi^a$ is true and $k > N_{\min} = n_j$ and, $G_k \le \epsilon$ will only cause it to exit earlier therefore it has $p_j \le \max(\bar p, n_j)$. 

@@

            If $p_{j - 1} \le \bar p /2$ then Line 14, 16 in Algorithm \ref{alg:linear-rgmapg} implies that $n_{j} \le \max(p_{j - 1}, 2p_{j - 1}) \le \bar p$. 

@@

                p_{j - 1} \ge \bar p /2 = \frac{2\sqrt{2L(1 + e)}}{\sqrt{\mu}} 
                \left \lfloor \frac{2\sqrt{\widehat L_k(1 + e)}}{\sqrt{\mu}} \right\rfloor. 

@@

                e^{-1} \ge 
                \frac{
                    F\left(x_{p_{j - 1}}^{(j - 1)}\right) - F^+
                {
                    F\left(x_{-1}^{(j - 1)}\right) - F\left(z_{p_{j - 1}}^{(j - 1)}\right)

@@

            Suppose that since the $j\ge 2$ th iteration, there is no period doubling for $T_\epsilon$ number of iterations in the outer loop of Algorithm \ref{alg:linear-rgmapg}, i.e: $n_{j + k + 1} = p_{j + k}$ for $ 0 \le k \le T_\epsilon - 1$.

        \end{proof}
        \begin{theorem}[bounds on the total iterations]
            ...
        \end{theorem}
        \begin{proof}

        \end{proof}
        \begin{theorem}[convergence rates of restarted GMAPG]
